---
title: "Nina Hernandez"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(openintro)
library(moderndive)
library(mosaic)
library(ggpubr)
library(infer)
```

## GitHub Documents

A quick glance at a dataset from the fivethrityeight package: mariokart

## Mariokart Auction Data

Brief summary statistics of each variable in the dataset. 

```{r cars}
summary(mariokart)
```

## Scatter Plot: Comparing Two Variables in Dataframe

This plot shows the relationship between the total number of bids a mario kart game received and the total price that game sold for, for both used and new condition mario kart games.

```{r pressure, echo=FALSE}
parallel_slopes_model <- lm(total_pr ~ n_bids + cond, data = mariokart)
summary(parallel_slopes_model)

ggplot(mariokart, aes(n_bids, total_pr, col=cond)) + geom_point() + 
  coord_cartesian(ylim = c(0,150)) +
  geom_abline(slope =0.5190, intercept = 46.4699-6.1549, col= "#00BFC4")  +
  geom_abline(slope = .5190, intercept = 46.4699, col= "#F8766D" ) +
  labs(x="Total Number of Bids", y="Total Price of Game", title = "Total Number of Bids vs. Total Price Of Mario Kart Game Based On Condition")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
